---
site: bookdown::bookdown_site
title: 'Comparison of Multivariate Estimation Methods'
date: "`r Sys.Date()`"
author:
  - name: Raju Rimal
    email: raju.rimal@nmbu.no
    affiliation: KBM
    footnote: Corresponding Author
  - name: Trygve Almøy
    email: trygve.almoy@nmbu.no
    affiliation: KBM
  - name: Solve Sæbø
    email: solve.sabo@nmbu.no
    affiliation: KBM
address:
  - code: KBM
    address: Faculty of Chemistry and Bioinformatics, Norwegian University of Life Sciences, Ås, Norway
classoption: ["12pt", "3p", "authoryear"]
monofont: 'sourcecodepro'
monofontoptions: "Scale=0.7"
colorlinks: true
linespacing: 1.5
fontfamily: mathpazo
use-landscape-page: yes
tables: yes
bibliography: 'References.bib'
biblio-title: References
biblio-style: elsarticle-harv
link-citations: true
github-repo: 'therimalaya/04-estimation-comparison'
always_allow_html: true
url: 'http\://therimalaya.github.io/04-estimation-comparison'
knit: 'bookdown::render_book'
review: yes
keywords: ['model-comparison', 'multi-response', 'simrel', 'estimation', 'estimation error', 'meta modeling', 'envelope estimation']
abstract: |
  Prediction performance does not always reflect the estimation behaviour of a method. High error in estimation may necessarily not result in high prediction error, but can lead to an unreliable prediction if test data lie in a slightly different subspace than the training data. In addition, high estimation error often leads to unstable estimates, and consequently, the estimated effect of predictors on the response can not have a valid interpretation. Many research fields show more interest in the effect of predictor variables than actual prediction performance. This study compares some newly-developed (envelope) and well-established (PCR, PLS) estimation methods using simulated data with specifically designed properties such as Multicollinearity in the predictor variables, the correlation between multiple responses and the position of principal components corresponding to predictors that are relevant for the response. This study aims to give some insights into these methods and help the researchers to understand and use them for further study. Here we have, not surprisingly, found that no single method is superior to others, but each has its strength for some specific nature of data. In addition, the newly developed envelope method has shown impressive results in finding relevant information from data using significantly fewer components than the other methods.
---

```{r, echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE}
suppressMessages({
  source("scripts/00-function.r")
  source("scripts/01-setup.r")
})
knitr::opts_chunk$set(comment = NULL, out.width = "100%", echo = FALSE)
if (knitr::is_html_output()) {
  knitr::opts_chunk$set(dev = 'svg', fig.retina = 2, dev.args = list(family="mono"))
}
```

```{r}
options(digits = 3, scipen = 999)
suppressMessages({
  source("scripts/03-collection.r")
})
```

# Introduction #

Estimation of parameters in linear regression models is an integral part of many research studies. Research fields such as social science, econometrics, chemometrics, psychology and medicine show more interest in measuring the impact of certain indicators or variable than performing prediction. Such studies have a large influence on people’s perception and also help in policy-making and decisions. A transparent, valid and robust research is critical to improving the trust in the findings of modern data science research [@eu2019auethics]. This makes the assessment of measurement error, inference and prediction even more essential.

Technology has facilitated researchers to collect large amounts of data, however, often such data either contains irrelevant information or are highly redundant. Researchers are devising new estimators to extract information and identify their inter-relationship. Some estimators are robust towards fixing the multicollinearity (redundancy) problem, while others are targeted to model only the relevant information contained in the response variable.

This study extends [@rimal2019pred] with a similar multi-response, linear regression model setting and compares some well-established estimators such as Principal Components Regression (PCR), Partial Least Squares (PLSR) Regression, together with two new methods based on envelope estimation: Envelope estimation in predictor space (Xenv) [@cook2010envelope] and simultaneous estimation of the envelope (Senv) [@cook2015simultaneous]. The estimation processes of these methods are discussed in the [Estimation Methods] section. The comparison is aimed at the estimation performance of these methods using multi-response simulated data from a linear model with controlled properties. The properties include the number of predictors, level of multicollinearity, the correlation between different response variables and the position of relevant predictor components. These properties are explained in the [Experimental Design] section together with the strategy behind the simulation and data model.
