%review=doublespace preprint=single 5p=2 column
\documentclass[12pt,3p,authoryear]{elsarticle}

%% add packages %%
%% ------------ %%
\usepackage[hyphens]{url}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{caption}
\usepackage{subfig}
\usepackage{amssymb, amsmath}
\usepackage[inline]{enumitem}
\usepackage{float}
\usepackage{tabularx}
\usepackage[dvipsnames, table]{xcolor}
\usepackage{ifxetex, ifluatex}
\usepackage{fixltx2e}
\usepackage[unicode=true, colorlinks]{hyperref}
\usepackage{cleveref}
\usepackage{tabu}
\usepackage{mathpazo}
%% ------------ %%

%% Conditional Packages %%
%% -------------------- %%

\usepackage{easyReview}



% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}


\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}



    \setmonofont{sourcecodepro}


\fi

% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}






\usepackage{longtable}




% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{5}

%% Use Landscape Pages
\usepackage{lscape}

\usepackage{setspace}
\setstretch{1.5}

\usepackage{lmodern}

%% -------------------- %%

%% Create and Provide some customizations %%
%% -------------------------------------- %%
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
  
%% Custom macros
\newtheorem{mydef}{Definition}
\newcommand{\bs}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\diag}[1]{\mathrm{diag}\left(#1\right)}
\newcommand{\seq}[3][1]{\ensuremath{#2_{#1},\ldots,\,#2_{#3}}}
\newcommand{\note}[1]{\marginpar{\scriptsize\tt{\color{RoyalBlue}#1}}}
\newcommand{\edit}[1]{{\color{OrangeRed} #1}}

%% Declare Operators
\newcommand{\argmin}{\operatornamewithlimits{arg\,min}}
\newcommand{\argmax}{\operatornamewithlimits{arg\,max}}

% set some lengths
\setlength{\parindent}{0pt}
% \setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

%% Hyperref color setup
\AtBeginDocument{%
  %% Define Colors
  \newcommand\myshade{80}
  \colorlet{mylinkcolor}{violet!\myshade!black}
  \colorlet{mycitecolor}{YellowOrange!\myshade!black}
  \colorlet{myurlcolor}{Aquamarine!\myshade!black}

  \hypersetup{
    breaklinks = true,
    bookmarks  = true,
    pdfauthor  = {},
    pdftitle   = {Comparison of Multivariate Estimation Methods},
    linkcolor  = mylinkcolor,
    citecolor  = mycitecolor,
    urlcolor   = myurlcolor,
    colorlinks = true,
  }
}
\urlstyle{same}  % don't use monospace font for urls
%% -------------------------------------- %%

%% Customizations %%
%% -------------- %%
 % turn line numbering on

%% -------------- %%

%% Configure Bibliography %%
%% ---------------------- %%
\bibliographystyle{elsarticle-harv}
\biboptions{numbers,sort&compress}

\makeatletter
\providecommand{\doi}[1]{%
  \begingroup
    \let\bibinfo\@secondoftwo
    \urlstyle{rm}%
    \href{http://dx.doi.org/#1}{%
      doi:\discretionary{}{}{}%
      \nolinkurl{#1}%
    }%
  \endgroup
}
\makeatother

% 

%% Header Includes %%
%% --------------- %%
%% --------------- %%



\begin{document}
%% --- Front Matter Start --- %%
\begin{frontmatter}

  \title{Comparison of Multivariate Estimation Methods}
  
    \author[KBM]{Raju Rimal\corref{c1}}
   \ead{raju.rimal@nmbu.no} 
   \cortext[c1]{Corresponding Author}
    \author[KBM]{Trygve Almøy}
   \ead{trygve.almoy@nmbu.no} 
  
    \author[NMBU]{Solve Sæbø}
   \ead{solve.sabo@nmbu.no} 
  
      \address[KBM]{Faculty of Chemistry and Bioinformatics, Norwegian University of Life
Sciences, Ås, Norway}
    \address[NMBU]{Prorector, Norwegian University of Life Sciences, Ås, Norway}
  
  \begin{abstract}
  Prediction performance often does not reflect the estimation behaviour
  of a method. High error in estimation not necessarily results in high
  prediction error but can leads to an unreliable prediction when test
  data are in a different direction than the training data. In addition,
  the effect of a variable becomes unstable and can not be interpreted in
  such situations. \textgreater{}\textgreater{} Fix from here
  \textless{}\textless{} Here we have extend the previous study on
  prediction comparison to compare the estimation of the methods used in
  the study.
  
  While Data science is battling to extract information from the enormous
  explosion of data, many estimators and algorithms are being developed
  for better prediction. Researchers and data scientists often introduce
  new methods and evaluate them based on various aspects of data. However,
  studies on the impact of/on model with multiple response model is
  limited. This study compares some newly-developed (envelope) and
  well-established (PLS, PCR) prediction methods based on simulated data
  specifically designed by varying properties such as multicollinearity,
  correlation between multiple responses and amount of information content
  in predictor variables. This study aims to give some insight on these
  methods and help researcher to understand and use them for further
  study.
  \end{abstract}
   \begin{keyword} model-comparison,multi-response,simrel\end{keyword}

\end{frontmatter}

\section{Introduction}\label{introduction}

Estimation of parameters in a regression model is an integral part in
many research study. Research fields such as social science,
econometric, psychology and medical study are more interested in
measuring the impact of certain indicator or variable rather than
performing prediction. Such studies has large influence in people's
perception and also help in policy making and decisions.

This study extends the {[}Refer to my current paper{]} and compares some
well established estimators such as Principal Components Analysis (PCA),
Partial Least Squares (PLS) together with two new methods based on
envelope estimation: Envelope estimation in predictor space (Xenv) and
simultaneous estimation of envelope (Senv). The comparison tests the
estimation performance of these methods using simulated data with
controlled properties. The properties includes the number of predictors,
level of multicollinearity, correlation between different response
variables and the position of relevant predictor components.

Prediction has been an essential components of modern data science,
weather it is statistical analysis or machine learning. Modern
technology has facilitated a massive explosion of data, however, such
data often contain irrelevant information consequently making prediction
difficult. Researchers are devising new methods and algorithms in order
to extract information to create robust predictive models. Mostly such
models contain predictor variables that are directly or indirectly
correlated with other predictor variables. In addition studies often
constitute of many response variables correlated with each other. These
interlinked relationships influence any study, whether it is predictive
modeling or inference.

Modern inter-disciplinary research fields such as chemometrics,
econometrics and bioinformatics are handling multi-response models
extensively. This paper attempts to compare some multivariate prediction
methods based on their prediction performance on linear model data with
specific properties. The properties includes correlation between
response variables, correlation between predictor variables, number of
predictor variables and the position of relevant predictor components.
These properties are discussed more in the {[}Experimental Design{]}
section. \citet{saebo2015simrel} and \citet{Alm_y_1996} have made a
similar comparison in the single response setting. In addition,
\citet{Rimal2018} has also made a basic comparison on some prediction
methods and their interaction with the data properties of a
multi-response model. The main aim of this paper is to present a
comprehensive comparison of contemporary prediction methods such as
simultaneous envelope estimation (Senv) \citep{cook2015simultaneous} and
envelope estimation in predictor space (Xenv) \citep{cook2010envelope}
with customary prediction methods such as Principal Component Regression
(PCR), Partial Least Squares Regression (PLS) using simulated dataset
with controlled properties. An experimental design and the methods under
comparison are discussed further, followed by a brief discussion of the
strategy behind the data simulation.


\renewcommand\refname{References}
\bibliography{ref-db.bib}


\end{document}
